---
  
Title: "Effects on Academic Performance"
Author: Vanya Trenado and Juana Jimenez
Date: April 8, 2023
output: github_document

---
## Introduction

When it comes to academic performance, one may think that everyone has the same opportunities to do a satisfactory job. However, this is not always the case. Most scholars get affected academically by factors such as their race, gender,income, schedules,culture and expectations from parents. using information obtained through three datasets we will be able to visualize the correlation between variables and the success of students. 

## Packages Required
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = TRUE)
```


```{r}
library(tidyverse) #used to tidy multiple data packages
library(ggplot2) #used for plotting
library(dplyr) #used for data manipulation
library(knitr) #used to dynamic report generation


student <- read.csv('C:\\Users\\vanya\\OneDrive\\Desktop\\Final_Project\\student_data01.csv')
glimpse(student)

performance <- read.csv('C:\\Users\\vanya\\OneDrive\\Desktop\\Final_Project\\student_performance.csv')
glimpse(performance)

satvsgpa <-read.csv('C:\\Users\\vanya\\OneDrive\\Desktop\\Final_Project\\sat_to_gpa.csv')
glimpse(satvsgpa)
```

## What gender and race got the higher grades percentage?

```{r}

```

## How did abcenses affect performance?

```{r}

```

## Effects of having a standard lunch vs free lunch
```{r}

```

## Did parents' education influence grades?
```{r}

```

## What student got the higher grade?
```{r}

```

##
## Conclusion

To summarize everything mentioned above, we have found that academic performance is not only based on the student. The environment in which the scholar is in plays a huge role in how good or bad he or she tries in school. Their parents might not have pursued a higher education so there is not much emphasis on the importance of doing well academically. 