---
  
Title: "Effects on Academic Performance"
Author: Vanya Trenado and Juana Jimenez
Date: April 8, 2023
output: github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)


student <- read.csv('C:\\Users\\vanya\\OneDrive\\Desktop\\Final_Project\\student_data01.csv')
glimpse(student)
```

When it comes to academic performance, one may think that everyone has the same opportunities to do a satisfactory job. However, this is sadly not the case. Most scholars get affected academically by factors such as their race, gender,income, schedules,culture and expectations from parents. The reasoning

```{r}

```

##

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

To summarize everything mentioned above, we have found that academic performance is not only based on the student. The environment in which the scholar is in plays a huge role in how good or bad he or she tries in school. Their parents might not have pursued a higher education so there is not much emphasis on the importance of doing wel academically. 